The Origin of the Virgo Overdensity

### 2012-07-24 2012-vod/draft.tex
updated vod

@@

We have validated our analysis technique with three different data sets: two high resolution spectroscopic libraries with exquisite S/N, and RGB stars in ten globular clusters observed on the AAT.

\subsection{Spectroscopic Libraries}
There is a growing number of high resolution spectroscopic libraries available for comparison, however few of them cover the spectral range covered by AAOmega's 1500V/1700D filter set.

>>>>

%Carlin et al ha a table of previously detected substructures (velocities, distances, fehs)

@@

We have validated our analysis technique with three different data sets. This includes two high resolution spectroscopic stellar libraries: the Indo-US library of Coude feed stellar spectra \citep[][hereafter CFLIB]{Valdes;et-al_2004}, and the Spectroscopic Survey of Stars in the Solar Neighbourhood \citep[][hereafter S$^{4}$N]{Allende_Prieto;et-al_2004}. These libraries sufficiently cover the spectral region covered by our observed configuration. As a further reference calibration, we observed AGB and RGB stars in ten globular clusters in our programme.

\subsection{Spectroscopic Libraries}
